Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-01-30 stp/paper_aaai/main.tex
Acronym KR in introduction

Firstly, we build a graph which includes attributes (i.e. columns) from the new
source as well as ontology classes and properties.
We name it \emph{integration graph}.
It uses information gathered from previously mapped data sources, and is further extended with information derived from the ontology.
%Firstly, we build a \emph{integration graph} which includes the 
%attributes from the new source as well as ontology classes and properties.
Secondly, we apply ML techniques to 
assign costs to its edges. 
Lastly, we use CP to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting 
Steiner Tree is a valid and coherent semantic model for the new source. 
Our contributions are:
%\begin{itemize}
	%\item 
	a novel modeling framework for the \relonto{} problem that uses ML, KRR and CP techniques;
%	\npr{symbolic AI, ontological reasoning, transitive closure}
	%\item
	an efficient approach to handle attributes which cannot be matched to 
	the ontology; \forijcai{through a new semantic labeling model and a new STP 
	model with additional nodes in the integration graph.}
	%\item 
	a flexible and extensible approach to the problem, easy to 
	reuse and adapt to specific situations through the use of CP.\forijcai{ allows introduction of additional constraints with no changes to the solver.} 
%\end{itemize}

>>>>

Firstly, we build a graph which includes attributes
% (i.e. columns) 
from the new
source as well as ontology classes and properties.
We name it \emph{integration graph}.
It uses information gathered from previously mapped data sources, and is further extended with information derived from the ontology.
%Firstly, we build a \emph{integration graph} which includes the 
%attributes from the new source as well as ontology classes and properties.
Secondly, we apply ML techniques to 
assign costs to its edges. 
Lastly, we use CP to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting 
Steiner Tree is a valid and coherent semantic model for the new source. 
Our contributions are:
%\begin{itemize}
	%\item 
	a novel modeling framework for the \relonto{} problem that uses knowledge representation, ML and CP techniques;
%	\npr{symbolic AI, ontological reasoning, transitive closure}
	%\item
	an efficient approach to handle attributes which cannot be matched to 
	the ontology; \forijcai{through a new semantic labeling model and a new STP 
	model with additional nodes in the integration graph.}
	%\item 
	a flexible and extensible approach to the problem, easy to 
	reuse and adapt to specific situations through the use of CP.\forijcai{ allows introduction of additional constraints with no changes to the solver.} 
%\end{itemize}
